---
title: "Class 11: Structural Bioinfomatics 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section 1. The PDB 

Q1: Determine the percentage of structures solved by X-Ray and Electron Microscopy. From the website what proportion of structures are protein? Aim to have a rendered GitHub document with working code that yields your answers.

```{r}
stats <-read.csv("Data Export Summary.csv", row.names = 1)
stats 
```

Total per row
```{r}
stats$Total
```

Total sum of all methods 
```{r}
sum(stats$Total)
```

How many of each? Percentage
```{r}
percentby.method <- stats$Total/sum(stats$Total) *100
names(percentby.method) <-  rownames(stats)
percentby.method
```

What percent of the data does proteins account for? 
```{r}
sum(stats$Proteins)/sum(stats$Total) * 100
```

Q2: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?
1338

## Section 3. Introduction to Bio3D in R

First we have to load the package we want to use 
```{r}
library(bio3d)
```

Now we can use 
```{r}
pdb <- read.pdb("1hsg")
```

```{r}
pdb
```

```{r}
attributes(pdb)
```

```{r}
head(pdb$atom)
```

```{r}
str(pdb)
```




```{r}
head( aa321(pdb$atom$resid))
```


We want to select out the protein and drug only parts of these molecular PDB files.
```{r}
protein.inds <- atom.select(pdb,"protein")
protein.inds
```

```{r}
prot.pdb <-  trim.pdb(pdb, prot.inds)
write.pdb(prot.pdb, file = "protein.pdb")
```

Lets do the same thing for our drug 
```{r}
lig.inds <- atom.select(pdb,"ligand")
lig.pdb <- trim.pdb(pdb, lig.inds)
write.pdb(lig.pdb, file = "ligand.pdb")
```

```{r}
install.packages("devtools")
devtools::install_bitbucket("Grantlab/bio3d-view")
```













