---
title: "Class 14: Genome Infomatics 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Asthma SNP in MXL population

Read file from Ensemble 


```{r}
mxl <-  read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")
head(mxl)
```

What are the genotypes here?
```{r}
mxl$Genotype..forward.strand.
```

How many of each genotype are in this set?
```{r}
table(mxl$Genotype..forward.strand.)
```

```{r}
table(mxl$Genotype..forward.strand.)/ nrow(mxl) *100
```

## RNA-Seq
Fastq quality scores 
Q. Does the first sequence have good quality?

```{r}
#install.packages("seqinr")
#install.packages("gtools")

q <- "DDDDCDEDCDDDDBBDDDCC@"
library(seqinr)
library(gtools)

asc( s2c(q)) - 33
```

## Population scale analysis 

Does the genotype for rs9067378 influence expression of the important asthma linked genes we found?
```{r}
geno <- read.table("rs8067378_ENSG00000172057.6.txt", row.names = 1)
head(geno)
```
How many G|G patients?
```{r}
table(geno$geno)
```

```{r}
inds <- geno$geno == "G/G"
summary(geno$exp[inds])
```

```{r}
inds.aa <- geno$geno == "A/A"
summary(geno$exp[inds.aa])
```

```{r}
inds.ag <- geno$geno == "A/G"
summary(geno$exp[inds.ag])
```

Some nice figure that shows the distribution of these expression values? 

```{r}
boxplot(exp ~ geno, geno)
```











